Making games from scratch is a long and difficult practice. Like most small development teams, we decided from day one that making a custom framework or engine would be inappropriate for the scope of the project. The team decided instead to make use of a commercial game engine. Using a commercial game engine puts a huge set of tools at our disposal, and allows for rapid prototyping and iterations. However, choosing which game engine to use is still a non-trivial solution. When choosing to use a commercial game engine, there are two major options: Unreal Engine 4 (developed by Epic Games) and Unity (developed by Unity Technologies). Both engines are excellent choices, and we carefully weighed their positive and negative attributes. 

Unreal Engine 4 is a high power tool. Written and scripted in C++, games shipped with Unreal can push the limits of the player's computer hardware. In addition Unreal is open source, includes better support for version control, and provides a very mature visual scripting system to aid in producing game logic. However, concerns were raised that Unreal would be too powerful for the needs of our project. Unreal's higher graphical fidelity is irrelevant in a sprite-based 2D application, and the engine's generally steeper learning curve threatened to greatly slow our progress in the project's early stages. In addition, Unreal's huge C++ code base can often result in very long compile times, especially for older development machines.

Unity is also an extremely advanced tool. Written in C++ and scripted with C\#, games made with Unity can generally be prototyped and iterated much faster than Unreal Projects. Unity easier to learn, has better documentation, more tutorials, and has vastly superior support for 2D titles. However, Unity's poor support for modern, non-proprietary version control systems borders inexcusable. The lack of a visual scripting tool can also prove cumbersome for some gameplay programming tasks that deal in more abstract ideas like game flow and artificial intelligence.

After extensive discussions, it was unanimously decided that \textit{Computron} will be built using Unity, version 2019.2.12.f1. Improved support for 2D titles and and superior ease of use were the deciding factors.



