Since this project will have real-world impacts, there are a number of
potential issues and precautions to address from the beginning. The fact that
this project is not sponsored and is not expected to generate any revenue
directly or indirectly suggests fewer potential legal issues than sponsored
projects or other projects that would provide a company with monetary gain. We have to
be careful of potential copyright infringement, since creating a game that is
very similar to existing games could introduce legal issues. If we use any
publicly available game assets, then we will have to ensure that we are
compliant with any terms of use. We plan on using original artwork for the game,
and the art will have to be royalty free, along with all other game assets.
Another legal consideration is the fact that members of our group have had to
sign non-disclosure agreements with multiple large companies relating to past
employment, but this is not expected to cause any issues at this time.\\

Ethical considerations must be made for our game and the testing we perform for
development. In order to optimize the educational capabilities of the game, we
are conducting tests on as many unaffiliated individuals as we can throughout
the development process. When performing any psychological tests, it is
important to create and maintain a controlled environment. Participants will be 
given a waiver to sign before they participate. For the sake of simplifying
the process and minimizing liability, we will not be performing these tests on
minors nor will we include minors in our target audience. Since the target
audience for our game is primarily college freshmen with little to no prior 
experience with Computer Science and computational thinking, we are able to 
set the target age at over 18, while also expecting that the game will be useful 
for a number of younger students in the middle and high school range.\\

Our team strongly supports the universal right to privacy for all people, and
our product will reflect that. No personally identifiable information will be
intentionally collected or stored about users. If our project includes a web
component and/or remote database, all data will be encrypted while in transit
or at rest. If we need to create user accounts and/or collect user email
addresses for scalability to verify user accounts, then those will have to be
encrypted and stored securely. If we do need to collect data from users, we 
will minimize the required information collected.\\