Since this project may have real-world impacts, there are a number of potential issues and precautions to address. The fact that this project is not sponsored and is not expected to generate any revenue directly or indirectly lends to fewer potential legal issues than projects that would provide a company with monetary gain. In that regard, there are still considerations in regards to rights of ownership of original artistic work that was created for this project. All of the artwork featured in the game is completely original work done by student artists Conner Ramputi and Christian Babcock. It was created explicitly for use in \textit{Computron} and its use or distribution elsewhere is completely reliant on individual artist consent. All music and sound for the game was designed by team member John Billingham. Its reproduction and distribution is also dependent on his express consent.\\

Ethical considerations were made for our game and the testing we performed during development. In order to optimize the educational capabilities of the game, we conducted tests on as many unaffiliated individuals as we could throughout the development process. We strongly encourage any future teams that take on this project to do the same and follow best practices when conducting playtesting sessions. If performing any psychological tests, it is important to create and maintain a controlled environment. For the sake of simplifying the process and minimizing liability, we have avoided performing these tests on minors and our target audience does not include minors. Since the target audience for \textit{Computron} is primarily college freshmen with little to no prior experience with computer science topics or computational thinking, we are able to set the target age at over 18, while also expecting that the game will be useful for a number of younger students with a similar skill range.\\

Our team strongly supports the universal right to privacy for all people, and our product reflects that. No personally identifiable information is collected or stored about users. If future versions of this project include a web component and/or remote database, all data should be encrypted while in transit or at rest. If there is a need to create user accounts and/or collect user email addresses for scalability to verify user accounts, then those will have to be encrypted and stored securely. If ever there is a reason to collect data from users, the required information collected should be minimized and only include what is absolutely necessary.