\subsection{Overview}
The purpose of this project is to provide a bridge for potential computer scientists to learn and explore the fundamentals of solving problems computationally. Providing this insight is non-trivial, especially in traditional teaching environments. Our approach is to present common introductory computer science concepts in the form of puzzles and visuals in a 2D video game. This game will provide a means for those interested in computational thinking to learn in a fun and engaging environment. The players will not be expected to set up a development environment or learn the nuances of specific programming languages. All of the concepts necessary to solving the challenges should be taught to -- or discovered by -- the player through interactive game play. Framing this tool as a game is an important distinction, as it allows us to deliberately craft the experience of the player and deliver specific learning outcomes.\\

Currently, there are many game offerings that focus on teaching computational thinking, with most of them focusing on using “code” solutions for puzzle solving. However, we have found that they tend to fall far on either end of a spectrum; either the game is too abstract and the computational thinking aspect is not well emphasized, or the game is too technical and therefore inaccessible to beginner level programmers. It is our intention to provide a game that falls between these two extremes on the spectrum. We have designed our game to teach the user about different commands and how they can be used to solve the puzzles provided. This will lean away from some of the more abstract puzzle-solvers, where the movements manipulate a character spatially instead of using the sequence of commands to solve the puzzle. Conversely, we will use clear and simple language coupled with visual and audio cues to explain commands and data structures in the game, while abstracting the intricacies of language specific commands or complex details about these elements. This will help new programmers to more easily understand the concepts of computer science and use them to solve the puzzles without requiring them to be familiar with language specific syntax or the complexities of managing data structures in code. For example, we can provide a heap data structure for them to use and explain its general purpose for sorting and storing data without forcing the user to construct or maintain the heap. Taking away the technical aspects of utilizing these elements will allow players to focus on learning and understanding the concepts of the tools they are given and how to utilize those tools to solve the problem presented.\\

\subsection{Broader Impacts}

The audience that \textit{Computron} is geared towards are people with very little technical experience relating to computer science and are just beginning to study how to program and learn computational logic. The aim of this project is to create an engaging platform for players to explore the process of approaching and solving problems computationally, build a foundation for understanding the principles of computer science, and prepare users for challenges they may face in their future studies of computer science.\\

At UCF, the difficulties that surround new computer science students are easily seen in the courses leading up to the Foundation Exam, perhaps most obviously with Introduction to C. Students in that class are immediately faced with two major tasks: learn to solve problems programmatically and learn the structure and syntax of the C programming language. Students often enter the class without any experience with either of these tasks, and many students end up feeling lost and discouraged early on.\\

Another aspect that should be considered is the unfortunate number of underrepresented groups in STEM fields, especially computer science. There are many factors that can contribute to this issue, such as individual backgrounds, ethnicity, gender, social stigmas, disabilities, or the common lack of preparation from underfunded public schools. Students who are already facing pressures related to these issues may be more inclined to give up on computer science when they feel lost in their first year.\\

As with any group of technically proficient individuals, it is not uncommon to find that a number of the more experienced members inadvertently reinforce a “gatekeeping” mindset towards STEM majors by supporting weed out classes and survival of the fittest. This behavior can occur with upper level computer science students or graduates who have seen the large number of highly intelligent students who give up on computer science, which could often be avoided if better education and resources were widely available.\\

For situations like any of those described above, a resource that can provide the tools necessary to understand and approach the concepts and challenges of computer science in an effective manner would be an invaluable resource for many individuals. Our project will provide these tools in an engaging format, enabling players of different backgrounds and experience levels to cultivate an intuitive understanding of computational thinking, while giving them a platform to apply their newfound perspective to approach and solve various problems. As a result, we hope that \textit{Computron} and similar resources help more students of all backgrounds in successfully pursuing their passion for computer science.\\

While the game strives to close the bridge between logic and syntax, by focusing on the former it can benefit a broader scope of people, regardless of if they plan to become software developers or simply wish to learn the logic of computer systems. The puzzles can act as a means to spark users’ interest in computer science, or just to be enjoyed by a spectrum of developers and engineers -- from students to industry professionals -- as the levels scale in complexity. Introducing a variety of puzzles that are solved using similar methods and mechanics will help players to begin recognizing similar patterns between different problems.\\

The game will have an engaging and easy to use interface to provide educational value with puzzle-based challenges. The mechanics of the game will be simple, since learning to play the game should not feel like a difficult task on its own. The scaling of puzzle difficulty will allow \textit{Computron} to be welcoming to beginners by incrementally introducing higher complexity tools and abilities as the levels progress. By providing feedback on the basic runtime and space complexities of working solutions, players will have the ability to learn how to solve problems efficiently.\\

\subsection{Personal Motivations}
\subsubsection{John Billingham}
Coming from having no programming experience prior to college, I have seen and experienced the disconnect between learning the correct syntax of a programming language and being able to think and solve problems programmatically. This game has an aim to teach basic logic and computational thinking skills to its users and I believe that this can close that specified gap that many of us have felt.

\subsubsection{Brandy King}
With career goals of being an Instructor of computer science, I was immediately intrigued during this project proposal. As a Teaching Assistant, I have spent a lot of time working with students in introductory level computer science courses. It is often a difficult subject for students who come in with little to no experience, and I have watched many students struggle with learning a new programming language at the same time that they are learning to use that language to effectively solve problems that they have been presented. I loved
the idea of an interactive game that would not only help teach people some of the basics, but also reinforce efficient problem solving with computational logic. I hope that the finished project we aim to provide will help students entering computer science classes by giving them confidence in their knowledge of concepts.\\

I am also very excited to learn new technologies, work with a team, and experiment with game development. As it currently stands, most of my experience with software development has been strictly course driven. Balancing full time studies, a full-time work schedule, and a family and personal life leaves me with extremely limited free time to pursue personal projects or devote time to learning things outside of lectures. Working on this project will give me the opportunity to expand my knowledge in a new programming language and to workwith a game engine. I have always been enthusiastic about video games, and I see their value as an engaging form of media. Being able to use this platform to convey instruction in computer science is a marriage of two things I am very passionate about.\\

\subsubsection{Nicolas LaCognata}
I pitched this project, and I care a great deal about it. I centered my undergraduate studies around games and simulations, and I’m excited to apply my knowledge to create a game that is both highly engaging and educational. There have been many occasions where my desire to pursue a career in game development has been viewed negatively, and I’d like to be able to point to this project as proof that the skills I have learned can provide a valuable experience to others.\\

The idea for this project mainly came from my experience as a Teaching Assistant for Intro to C. When I took the class, I had prior programming experience. For much of the class I checked out mentally. I drifted through the class without really seeing what was going on. Going back and seeing the challenges new programmers really face was a profound experience. I want this game to help aspiring programmers, and spark interest in our field for those on the outskirts.

\subsubsection{Sean Simonian}
Like many computer science students, I had very little programming experience and next to zero understanding of most computer science concepts when I first started at UCF, and I quickly found myself struggling immensely with the introductory computer science courses. The main reason I was able to get through the first year of computer science courses was because of friends who were willing to help tutor me in the areas where the lectures were not effective enough at explaining concepts to beginners. In later years, I became a much better computer science student, and found myself in the opposite role as before. I have had the opportunity to serve as a mentor to other students struggling with computer science, and often tutored several people whose professors’ teaching styles failed to meet the needs of the students. By experiencing both sides of these situations, I have learned quite a bit about what beginners struggle with when learning computer science concepts, and how these concepts need to be broken down and taught in relatable ways. I am excited about the opportunity to create a tool that can help individuals build a strong foundation for understanding computer science.\\

Video game development was the primary reason I decided to study computer science, which motivated me to learn to create a video game for my high school senior project, and joined the Game Dev Knights club at UCF during my freshman year. Later I moved away from the goal of game development in favor of interests in software development and cyber security, so this project will provide the opportunity to more thoroughly explore game development in a real setting with a team without having to change the direction of my studies or career path.\\

My technical experience includes working as a software engineer for Harris Corporation supporting programs for the Federal Aviation Administration, and later working as a software developer for Texas Instruments supporting their internal Data Lifecycle Management project. I have also completed a minor in Secure Computing and Networks, have been an active member of UCF’s Collegiate Cyber Defense Club for the past few years, and am currently part of the operations team for Hack@UCF to support the club. Each of these experiences has helped me build various skills that should be useful for this project. Working on this game will provide the opportunity to develop additional skills in areas where I would otherwise be lacking.\\
